Spin canonical divisors of log stacky curves

### 2015-07-01 stacky_write_up/spin_cring.tex
editing background, up to sat

\makeatletter
\newcommand{\customlabel}[2]{%
   \protected@write \@auxout {}{\string \newlabel {#1}{{#2}{\thepage}{#2}{#1}{}} }%
   \hypertarget{#1}{#2}
}
\makeatother

@@

Let $X$ be a smooth algebraic curve of genus $g$ over a field $k$.
It is well known that the canonical sheaf $\Omega _X,$ with
associated canonical divisor $K_X$, determines the {\bf canonical
map } $\pi: X \rightarrow \BP_k^{g - 1}$. Then, the {\bf canonical
ring} is defined to be
\begin{align*}
	R(X, K_X) = \bigoplus_{d \geq 0} H^0(X, dK_X),
\end{align*}

@@

\begin{rem}
\label{rem:main-weaker-assumptions}
In fact, the proof of Theorem ~\ref{thm:main} holds not only for log divisors, which must have distinct points, but also for arbitrary effective divisors
$\Delta$. Furthermore, one may view stacky curves as stacks, in which case one only need assume that the stacky curve
is separably rooted, i.e. the residue field at each stacky point
is separable.
\end{rem}

@@

\todo{Somewhere in the paper, we should probably give an example showing the generators and relations are sharply bounded at degree e, 2e. Robin: Aren't the base cases suitable examples? Aaron: Those don't show it for general e, do they? I don't think we really need an example, just a remark somewhere that one cannot really hope to do better than e, 2e somewhere.}

\section{Background}
\label{sec:background}
Here we collect various definitions and useful notation that will be
used throughout the paper. Many of the conventions come from existing
literature. For basic references on the statements and definitions
used below, see Hartshorne \cite[Chapter IV]{hartshorne:ag},
Saint-Donat \cite{saint-donat:proj}, the book of Arbarello--
Cornalba--Griffiths--Harris \cite[Section III.2]
{acgh:algebraic-curves}, and Voight--Zureick-Brown \cite[Chapter 2,
Chapter 5]{vzb:stacky}.

@@

When viewed in the formalism of stacks, all stacky curves will be assumed to be tame and
$k$ will always be algebraically closed. We also assume that the
stacky curves are separably rooted, i.e. the residue field of each
of the stacky points is separable.

With the close relation to stacks in mind, for simplicity, the remainder of this paper is primarily phrased using the language
of Weil divisors.
\end{rem}

If $P_1, \ldots, P_r$ are the stacky points of a stacky curve $\sx$,
then we use $e_1, \ldots, e_r \in \BZ_{\geq 2}$ to denote the orders
of the stabilizer groups of the points with non-trivial
stabilizers. We call $e_i$ the \textbf{stabilizer order} of $P_i$.
In order to study objects associated with stacky curves, it is often
useful to consider them in the context of ordinary schemes.

\begin{defn}
\label{defn:coarse-space}
Let $\sx$ be a stacky curve over $k$ with stacky points $P_1, \ldots,
P_r$ with stabilizer orders $e_1,\ldots, e_r \in \BZ_{\geq 2}$.
Let $X$ be a nonsingular projective (algebraic) curve over $k$ of
genus $g$. Then $X$ is the \textbf{coarse space} associated to $\sx$
if

\[
	\di \sx = \left(\bigoplus_{P\notin \{P_1,\ldots, P_r\}} \langle 
	P \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left \langle 
	\frac{1}{e_i}P_i \right \rangle \right) \subseteq \BQ \otimes \di X.
\]
\end{defn}

We can equip stacky curves with a divisor $\Delta$ that is a 
sum of distinct points each with trivial stabilizer. A divisor
$\Delta$ of this form is called a \textbf{log divisor}. We use
$\delta := \deg \Delta$ to refer to the degree of the log divisor.
If $\sx$ has coarse space $X$ of genus $g$, then we say $\sx$ has
\textbf{signature} $\sigma = (g; e_1, \ldots, e_r; \delta)$.

The pairs $(\sx, \Delta)$ are called \textbf{log stacky curves}
and the study of their canonical rings is the main focus of
the work by Voight and Zureick-Brown \cite{vzb:stacky}.
For this paper, we consider \textbf{log spin curves} which are
triples $(\sx, \Delta, \halfcan)$ where $\Delta$ is a log divisor
and a divisor $\halfcan$ which satisfies the property that
$2\halfcan \sim K_\sx + \Delta$. Such a divisor $\halfcan$
is called a \textbf{log spin canonical divisor} on $(\sx, \Delta)$. 
We also use $\halfcan_X$ to refer to the spin canonical divisor
(also known as the half-canonical divisor, semi-canonical divisor, 
or a theta characteristic in other literature) associated with the
coarse space $X$ of $  \sx$, i.e. $\halfcan_X$ is a divisor such
that $2\halfcan \sim K_X$. Furthermore, we use the following
analogous notations:

@@

@@

@@

\noindent
When the log spin curve is fixed, we usually use $R$ or $R_\halfcan$ to
represent $R(\sx, \Delta, \halfcan)$. We also often use $H^0(\sx, D)
:= H^0(\sx, \sco(D))$ and $h^0(\sx, \sco(D)) := \dim H^0(\sx, \sco(D))$.
If $R$ is a graded ring, then we let $(R)_d$ refer to the $d^\text{th}$
degree component of $R$.

\todo{Note that this result is independence of base field}

@@

\noindent
where $a_i \in \BZ$ and $e_i$ are odd. This is due to the fact
that $\halfcan \in \di \sx$ by Kodaira--Spencer
\cite{kodaira-spencer:deformations}. If $e_i$ were even,
then $\frac{e_i - 1}{2e_i}$ would be in reduced form and
the denominator would be too large for $\halfcan$ to be
in $\di \sx$.
\todo{refine above}
\end{rem}

\begin{rem}
\label{rem:delta-not-1}
Suppose $(\sx, \Delta, \halfcan)$ is a log spin curve. Note that $\deg \Delta$
is even. because $2 \cdot \deg \halfcan = \deg \Delta + \deg \lfloor K
\rfloor = \deg \Delta + 2(g-1).$ Therefore, $\deg \Delta$ is even.
In particular, we shall often use $\deg \Delta \neq 1$.
\end{rem}

\begin{defn}
\label{def:order-sup}
If $z$ is a rational section of $\sco(D)$ denote the order of
zero of $z$ at $P$ by $\ord_P^D(z)$.
\end{defn}
\todo{where to put above?}

We define the notion of the saturation of a divisor, taken from
Voight and Zureick-Brown ~\cite[Section 7.2]{vzb:stacky}.

@@

\begin{defn}
\label{defn:sat}
The \textbf{saturation} for a monoid $M \subseteq \BZ_{\geq 0}$,
denoted $\sat(M)$, is the smallest integer $s$ such that $M
\supseteq \BZ_{\geq s}$, if such an integer exists.
\end{defn}

\begin{rem}
For our purposes, it is useful to call the saturation of the
effective monoid of a divisor $D$ as the saturation $s$ of the
divisor $D$ on $\sx$. In this case, the saturation $s :=
\sat(\Eff(D))$ of a divisor $D$ on $\sx$ is the smallest positive
$s \in \BZ$ such that $\deg \lfloor dD \rfloor \geq 0$ for all $d
\geq s$.
\end{rem}

@@

First, we give a definition of the graded degree of a monomial
in a graded polynomial ring.

\begin{defn}
\label{defn:monomial-degree}
Let $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$ be a graded polynomial
ring and let $\alpha := \prod_{i = 1}^{n} x_{d_i, i}^{f_i} \in
k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$ be a monomial. Then
we define
\[
	\deg \alpha := \sum_{i = 1}^{n} d f_i.
\]
\end{defn}

@@

@@

\noindent
with each $y_{i, e_i'}$ viewed in $R'$ through the image of this isomorphism and such that for each $i \in J$ such that the following
three conditions hold:
\begin{enumerate}
	\item[\customlabel{Ad-i}{(Ad-i)}] First, 
	\begin{align*}
	\deg y_{e_i'} &= e_i'  &\text{ and } &&-\ord_{Q_i}^{\halfcan_X'}(y_{i, e_i'})
		= \frac{e_i'- 1}{2}.
	\end{align*}
		\item[\customlabel{Ad-ii}{(Ad-ii)}] Second, every generator $z \in \{x_1, \ldots, x_m\} \cup \{y_{j,e_ij'}: j\in J - \{i\} \}$ satisfies
		\begin{align*}
			\frac{-\ord_{Q_i}
^{\halfcan_X'}(z)}{\deg z} < \subhalf {e_i'}.
		\end{align*}
	\item[\customlabel{Ad-iii}{(Ad-iii)}] Third, we have
		\begin{align*}
			\deg \lfloor e_i L' \rfloor \geq \max(2g - 1,0) + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
		\end{align*}
		where
		\begin{align*}
			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
			\mid e_i - e_j'\}.
		\end{align*}
\end{enumerate}
\end{defn}

@@

Now, we check admissibility. By relabelling the
variables if necessary, we can assume that $x_{7, 1}$ corresponds
to the generator with maximal pole order at $P_2$ and $x_{7, 2}$
correspond to the generator with maximal pole order at $P_3$. Use
the presentation given above with $y _{2, e_2'} := x_{7, 1}$ and
$y_{3, e_3'} :=  x_{7, 2}$. We see that it immediately satisfies
\ref{Ad-i} of Definition ~\ref{defn:admissible}. Next we check \ref{Ad-ii} We may also choose
pole orders of the generators such that $y_{i, e_i'}$ is the only
generator lying on the line $-ord_{P_i}(z) = \deg z \frac{3d}{7}$
in the $(\deg z, -ord_{P_i}(z))$  lattice and with the other
generators lying below the line as seen in Figure ~\ref{fig:377}
(e.g. the pole orders $(-ord_{P_1}(z)$, $-ord_{P_2}(z)$, $-ord_{P_3}
(z))$ may be chosen to be $(1, 1, 1)$, $(1, 2, 2)$, $(2, 3, 2)$,
and $(2, 2, 3)$ for $z = x_{3, 1}$, $x_{5, 1}$, $x_{7, 1}$, and
$x_{7, 2}$ respectively).

@@

Also note that $e_j' + 2d = 7 + 2d \nmid 2 = e_i - e_j'$ for all
$i, j \in J = \{2, 3\}$ such that $j \neq i$ and for all $d \geq
0$. Thus, $s_{\sigma, J}(i, d) = \emptyset$ for each $i \in J$.
Furthermore, $\deg \lfloor e_i \halfcan \rfloor = \deg \lfloor 9
\halfcan \rfloor = 2 \lfloor \frac{4 \cdot 9}{9} \rfloor + \lfloor
\frac{9}{3} \rfloor - 9 = 2$, so \ref{Ad-iii} is satisfied and
$(\sigma, \sx', J)$ is admissible.

@@

We next check $(\sx', \halfcan',\{1,2\})$ is admissible. We have two generators $x_3$ and $y_3$ in degree 3 with a pole of order $1=\frac{3- 1}{2}$ by construction. Hence, \ref{Ad-i} holds. We next check \ref{Ad-ii} for the point $P_1$, as the case of $P_2$ is symmetric. Here, by construction
$$
\frac{-\ord_{P_1}(z)}{\ord(z)} = \begin{cases}
	0 &\text{ if }z \in \{u, y_3\}\\
	\frac{1}{4} &\text{ if }z = y_4
\end{cases}.$$
Since $0 < \frac{1}{4} < \frac{1}{3}$, \ref{Ad-ii} holds.
Finally, to check \ref{Ad-iii}, note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = 2 \cdot 1 - 1 + 0$.
\end{example}

@@

%\begin{rem}
%Note that $S_{\sigma,J}(i,d-1)$ as defined in condition \ref{Ad-iii} of Definition ~\ref{defn:admissible} can equivalently be defined as $S_{\sigma,J}(i,d-1)= \{j \in J : j \neq i \text{ and }(e_j' + 2d-2)|e_i' + 2d\}.$ Written this way, $\# S_{\sigma,J}(i,d-1)$ is more apparently similar to $\mu(i,d)$ as defined in \cite[Defintion 8.5.1]{vzb:stacky}.
%\end{rem}
%\todo{Peter: I'm not sure how useful this remark is.  After seeing the definition of $S_{\sigma, J}(I,d)$ a reader will probably be a little mystified why it is a useful condition.  The inclusion of the relationship to something defined in VZB that also seems ad hoc and that they probably will not have seen may not be the most helpful use of this space.}

%\begin{lem}\label{lem:n-3s-admissible}
%Fix a genus $g$, a log divisor $\Delta$, and a coarse space $X$. Suppose $3\le r\in \BN$ so that all stacky curves $\sx'$ with $r- 1$ stacky points of degree 3 over the coarse space $X$ have all subsets $J'$ of $\{e_1, \ldots, e_{r- 1}\}$ admissible in $L'$. Then if $\sx$ has coarse space $X$, any subset of $J$ of $\{e_1, \ldots, e_r\}$ (with all $e_i =3$) is admissible viewed in $L$.
%\end{lem}
%\begin{proof}
%To show \ref{Ad-i} and \ref{Ad-ii} look at some $\sx'$ with $r- 1$ stacky points $'s=\{Q_1, \ldots, Q_{j - 1}, Q_{j + 1}, \ldots Q_r\}$ including a chosen $Q_i$ (and excluding some $Q_j\ne Q_i$). Then select $y_{e_r'}$ from the choice that makes the set $J'=\{i\}$ an admissible set in $\sx'$; this naturally can be seen inside of $R_{\sx}$ and satisfies \ref{Ad-i}. Furthermore, since $s$ is an admissible set of $L'$, in particular, we must have \ref{Ad-ii} satisfied so $\frac{-\ord_{Q_l}
%^{\halfcan_X'}(y_i)}{\deg (y_i)} = 0$ for\todo{I'm confused how \ref{Ad-ii} follows in genus 0?}
%
 %follows immediately from the base-point freeness of $3\halfcan$ which we have for the following reasons in the various genera:
%\begin{itemize}
%\item When $g> 0$, $\deg(\lfloor 3 L\rfloor)\ge 3g-3+2\ge 2g$ (the added two comes from the fact that $r\ge 2$).
%\item When $g= 0$, since $L'$ has a nontrivial admissible subset within $\{e_1, \ldots, e_{r- 1}\}$ satisfying \ref{Ad-i}, we know $\deg(\lfloor 3\lfloor)\ge 0$, so it is base-point free.
%\end{itemize}
%\end{proof}

The following Lemma will slightly strengthen condition \ref{Ad-ii} from Definition ~\ref{defn:admissible} and this improvement is crucially used in the proof of part (c) of Lemma ~\ref{lem:raise-stacky-order}.

\begin{lem}
\label{lem:admissible_inequality}
For any $z$ as in condition \ref{Ad-ii} of definition ~\ref{defn:admissible} the inequality \ref{Ad-ii} implies the
tighter inequality that

@@

\begin{proof}
We know by \ref{Ad-ii} that

@@

\begin{proof}
Each of the conditions \ref{Ad-i}, \ref{Ad-ii}, and \ref{Ad-iii} hold for $W$
if they hold for $J$.
\end{proof}

@@

\noindent
The assumption \ref{Ad-iii} implies
\begin{align*}
	\deg \left( e_i L' - E_i \right) \geq \max(2g - 1,0),
\end{align*}

@@

By part (a), condition \ref{Ad-ii}, and Lemma
~\ref{lem:admissible_inequality} we have
\begin{align*}
	-\ord_{Q_j}
^{\halfcan_X'}(y_{i, e_i})-\ord_{Q_j}
^{\halfcan_X'}(z)
	&\leq \frac{e_j - 1}{2} + \deg (z) \left( \subhalf{e_j'} \right) -\frac{1}{e_j'} \\
	& = \frac{e_j - 1}{2} -\frac{1}{e_j'} +\deg (z) \left( \subhalf{e_j'} \right) \\
	&= \frac{e_j(e_j -3)}{2(e_j -2)} +\deg (z) \left( \subhalf{e_j'} \right) \\
	&= \deg (y_{i, e_i}z) \subhalf{e_j'}.
\end{align*}

@@

{\bf Part (d):}
To check (d), we show \ref{Ad-i},\ref{Ad-ii}, and \ref{Ad-iii} are satisfied. We know \ref{Ad-i} holds by part (b), taking the $y_{
i, e_i}$ as the generators in degree $e_i$. Next, \ref{Ad-ii} is
strictly monotonic in the $e_i$ and hence also holds for $(\sx, J)$.
Finally, if \ref{Ad-iii} holds for $e$ then it holds for $e + 2$ by
definition. This is where we use that \ref{Ad-iii} holds for $d > 0$
and not just for $d = 0$.
\end{proof}

@@

\rm{
\begin{longtable}
	{| c || c | c | c |}
	\hline
	Case & Signature $\sigma$ & $J$ & $e$\\
	\hline
	\hline

	(a) & $(0; 3, 3, 11; 0)$ & $\{3\}$ & $11$ \\	\hline

	(b) & $(0; 3, 5, 9; 0)$ & $\{3\}$	& $9$ \\ \hline

	(c) & $(0; 3, 7, 7; 0)$ & $\{2, 3\}$ & $7$ \\ \hline

	(d) & $(0; 5, 5, 7; 0)$ & $\{3\}$	& $7$ \\ \hline

	(e) & $(0; 5, 7, 7; 0)$ & $\{2, 3\}$ & $7$ \\ \hline

	(f) & $(0; 7, 7, 7; 0)$ & $\{1, 2, 3\}$	& $7$ \\ \hline

	(g) & $(0; 3, 3, 3, 5; 0)$ & $\{4\}$ & $5$ \\ \hline

	(h) & $(0; 3, 3, 5, 5; 0)$ & $\{3, 4\}$ & $5$ \\ \hline

	(i) & $(0; 3, 5, 5, 5; 0)$ & $\{2, 3, 4\}$ & $5$ \\ \hline

	(j) & $(0; 5, 5, 5, 5; 0)$ & $\{1, 2, 3, 4\}$ & $5$ \\ \hline

	(k) &	$(0; 3, 3, 3, 3, 3; 0)$ & $\{1, 2, 3, 4, 5\}$ & $5$ \\ \hline

	\caption{Genus 0 Base Cases}
	\label{table:g-0-base-cases}
\end{longtable}
}

>>>>

@@

Let $X$ be a smooth algebraic curve of genus $g$ over a field $k$.
It is well known that the canonical sheaf $\Omega _X,$ with
associated canonical divisor $K_X$, determines the {\bf canonical
map } $\pi: X \rightarrow \BP_k^{g - 1}$. Then, the {\bf canonical
ring} is defined to be
\begin{align*}
	R(X,K_X) = \bigoplus_{d \geq 0} H^0(X, dK_X),
\end{align*}

@@

\begin{rem}
\label{rem:main-weaker-assumptions}
In fact, the proof of Theorem ~\ref{thm:main} holds not only for log divisors, which must have distinct points, but also for arbitrary effective divisors
$\Delta$. Furthermore, one may view stacky curves as stacks, in which case one may relax the assumption that $k$ is perfect. Instead, one only need assume that the stacky curve
is separably rooted, i.e. the residue field at each stacky point
is separable.
\end{rem}

@@

\section{Background}
\label{sec:background}
Here we collect various definitions and notation that will be
used throughout the paper. Many of the conventions come from existing
literature. For basic references on the statements and definitions
used below, see Hartshorne \cite[Chapter IV]{hartshorne:ag},
Saint-Donat \cite{saint-donat:proj}, Arbarello--
Cornalba--Griffiths--Harris \cite[Section III.2]
{acgh:algebraic-curves}, and Voight--Zureick-Brown \cite[Chapter 2,
Chapter 5]{vzb:stacky}.

For the remainder of this paper, fix an algebraically closed field $k$.
This is no restriction on generality, as generator and relation degrees are preserved under base change to the algebraic closue.

@@

In this paper, all stacky curves are assumed to be tame and
$k$ will is assumed to be algebraically closed. We also assume that the
stacky curves are separably rooted, i.e. the residue field of each
of the stacky points is separable.

With this stacks-theoretic description in mind, for simplicity, the remainder of this paper is primarily phrased using the language
of Weil divisors.
\end{rem}

If $P_1, \ldots, P_r$ are the stacky points of a stacky curve $\sx$,
then we use $e_1, \ldots, e_r \in \BZ_{\geq 2}$ to denote the orders
of the stabilizer groups of the points with non-trivial
stabilizers. We call $e_i$ the \textbf{stabilizer order} of $P_i$.
In order to study objects associated with stacky curves, it is often
useful to consider them in the context of schemes (instead of in the context of stacks).

\begin{defn}
\label{defn:coarse-space}
Let $\sx$ be a stacky curve over $k$ with coarse space $X$ and stacky points $P_1, \ldots,
P_r$ with stabilizer orders $e_1,\ldots, e_r \in \BZ_{\geq 2}$.
Let $X$ be a nonsingular projective (algebraic) curve over $k$ of
genus $g$. Then, we notate
\[
	\di \sx = \left(\bigoplus_{P\notin \{P_1,\ldots, P_r\}} \langle 
	P \rangle \right) \oplus \left(\bigoplus_{i = 1}^r \left \langle 
	\frac{1}{e_i}P_i \right \rangle \right) \subseteq \BQ \otimes \di X.
\]
\end{defn}

We can equip stacky curves with a log divisor $\Delta$ that is a 
sum of distinct points each with trivial stabilizer. A divisor
$\Delta$ of this form is called a \textbf{log divisor}. We use
$\delta := \deg \Delta$ to refer to the degree of the log divisor.
If $\sx$ has coarse space $X$ of genus $g$, then we say $\sx$ has
\textbf{signature} $\sigma = (g; e_1, \ldots, e_r; \delta)$.

@@

A pair of a stacky curve and a log divisor $(\sx, \Delta)$ is called a \textbf{log stacky curves}
and the study of their canonical rings is the main focus of
the work by Voight and Zureick-Brown \cite{vzb:stacky}.
For this paper, we consider \textbf{log spin curves} which are
triples $(\sx, \Delta, \halfcan)$ where $\sx$ is a stacky curve, $\Delta$ is a log divisor, and $\halfcan \in \di \sx$ satisfies
$2\halfcan \sim K_X + \Delta + \sum_{i=1}^{r}\frac{e_i-1}{e_i}P_i$. Such a divisor $\halfcan$
is called a \textbf{log spin canonical divisor} on $(\sx, \Delta)$. 
We use $\halfcan_X := \lfloor L \rfloor $ to refer to the spin canonical divisor
(also known as the half-canonical divisor, semi-canonical divisor, 
or theta characteristic) associated to the
coarse space $X$ of $\sx$, i.e. $\halfcan_X$ is a divisor such
that $2\halfcan_X \sim K_X + \Delta$. Furthermore, we use the following
analogous notation:

@@

\begin{rem}
Although Definition ~\ref{defn:h0-stacky} may seem fairly ad hoc, it is naturally motivated in the context of stacks. See Voight and Zureick-Brown \cite[Lemma 5.4.7]{vzb:stacky} for a proof that Definition ~\ref{defn:h0-stacky} is equivalent to the stack-theoretic description.
\end{rem}

@@

\noindent
When the log spin curve is fixed, we usually use $R$ or $R_\halfcan$ to
represent $R(\sx, \Delta, \halfcan)$. We also often use $H^0(\sx, D)
:= H^0(\sx, \sco(D))$ and $h^0(\sx, \sco(D)) := \dim_k H^0(\sx, \sco(D))$.
If $R$ is a graded ring, then we let $(R)_d$ refer to the $d^\text{th}$
graded component of $R$.

@@

\noindent
where $a_i \in \BZ$ and $e_i$ are odd. This is due to the fact
that $\halfcan \in \di \sx$. If some $e_i$ were even,
then $\frac{e_i - 1}{2e_i}$ would be in reduced form implying $\halfcan \notin \di \sx$.
\end{rem}

\begin{rem}
\label{rem:delta-not-1}
Suppose $(\sx, \Delta, \halfcan)$ is a log spin curve. Note that $\deg \Delta$
is even. because $2 \cdot \deg \halfcan = \deg \Delta + \deg \lfloor K
\rfloor = \deg \Delta + 2(g-1).$
In particular, we shall often use $\deg \Delta \neq 1$.
\end{rem}

\ssec{Definition of Saturation}

We define the notion of the saturation of a divisor, as defined in
Voight and Zureick-Brown ~\cite[Section 7.2]{vzb:stacky}.

@@

\begin{defn}
\label{defn:sat}
The \textbf{saturation} of a monoid $M \subseteq \BZ_{\geq 0}$,
denoted $\sat(M)$, is the smallest integer $s$ such that $M
\supseteq \BZ_{\geq s}$, if such an integer exists.
\end{defn}

\begin{rem}
For $D \in \di \sx$, we will often call $\sat(\Eff(D))$ the saturation of $D.$
\end{rem}

@@

First, we give a definition of the graded degree of a monomial
in a graded polynomial ring.
\todo{possibly compactify or refer to relations}
\begin{defn}
\label{defn:monomial-degree}
Let $k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$ be a graded polynomial
ring and let $\alpha := \prod_{i = 1}^{n} x_{d_i, i}^{f_i} \in
k[x_{d_1, 1}$, $\ldots$, $x_{d_n, n}]$ be a monomial. Then
we define
\[
	\deg \alpha := \sum_{i = 1}^{n} d f_i.
\]
\end{defn}

@@

\begin{defn}
\label{def:order-sup}
If $z$ is a rational section of $\sco(D)$ denote the order of
zero of $z$ at $P$ by $\ord_P^D(z)$.
\end{defn}

@@

\noindent
with each $y_{i, e_i'}$ viewed in $R'$ through the image of this isomorphism and such that for each $i \in J$ such that the following
three conditions hold:
\begin{enumerate}
	\item[(Ad-i)] First, 
	\begin{align*}
	\deg y_{e_i'} &= e_i'  &\text{ and } &&-\ord_{Q_i}^{\halfcan_X'}(y_{i, e_i'})
		= \frac{e_i'- 1}{2}.
	\end{align*}
		\item[(Ad-ii)] Second, every generator $z \in \{x_1, \ldots, x_m\} \cup \{y_{j,e_ij'}: j\in J - \{i\} \}$ satisfies
		\begin{align*}
			\frac{-\ord_{Q_i}
^{\halfcan_X'}(z)}{\deg z} < \subhalf {e_i'}.
		\end{align*}
	\item[(Ad-iii)] Third, we have
		\begin{align*}
			\deg \lfloor e_i L' \rfloor \geq \max(2g - 1,0) + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
		\end{align*}
		where
		\begin{align*}
			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
			\mid e_i - e_j'\}.
		\end{align*}
\end{enumerate}
\end{defn}

@@

Now, we check admissibility. By relabelling the
variables if necessary, we can assume that $x_{7, 1}$ corresponds
to the generator with maximal pole order at $P_2$ and $x_{7, 2}$
correspond to the generator with maximal pole order at $P_3$. Use
the presentation given above with $y _{2, e_2'} := x_{7, 1}$ and
$y_{3, e_3'} :=  x_{7, 2}$. We see that it immediately satisfies
(Ad-i) of Definition ~\ref{defn:admissible}. Next we check (Ad-ii) We may also choose
pole orders of the generators such that $y_{i, e_i'}$ is the only
generator lying on the line $-ord_{P_i}(z) = \deg z \frac{3d}{7}$
in the $(\deg z, -ord_{P_i}(z))$  lattice and with the other
generators lying below the line as seen in Figure ~\ref{fig:377}
(e.g. the pole orders $(-ord_{P_1}(z)$, $-ord_{P_2}(z)$, $-ord_{P_3}
(z))$ may be chosen to be $(1, 1, 1)$, $(1, 2, 2)$, $(2, 3, 2)$,
and $(2, 2, 3)$ for $z = x_{3, 1}$, $x_{5, 1}$, $x_{7, 1}$, and
$x_{7, 2}$ respectively).

@@

Also note that $e_j' + 2d = 7 + 2d \nmid 2 = e_i - e_j'$ for all
$i, j \in J = \{2, 3\}$ such that $j \neq i$ and for all $d \geq
0$. Thus, $s_{\sigma, J}(i, d) = \emptyset$ for each $i \in J$.
Furthermore, $\deg \lfloor e_i \halfcan \rfloor = \deg \lfloor 9
\halfcan \rfloor = 2 \lfloor \frac{4 \cdot 9}{9} \rfloor + \lfloor
\frac{9}{3} \rfloor - 9 = 2$, so (Ad-iii) is satisfied and
$(\sigma, \sx', J)$ is admissible.

@@

We next check $(\sx', \halfcan',\{1,2\})$ is admissible. We have two generators $x_3$ and $y_3$ in degree 3 with a pole of order $1=\frac{3- 1}{2}$ by construction. Hence, (Ad-i) holds. We next check (Ad-ii) for the point $P_1$, as the case of $P_2$ is symmetric. Here, by construction
$$
\frac{-\ord_{P_1}(z)}{\ord(z)} = \begin{cases}
	0 &\text{ if }z \in \{u, y_3\}\\
	\frac{1}{4} &\text{ if }z = y_4
\end{cases}.$$
Since $0 < \frac{1}{4} < \frac{1}{3}$, (Ad-ii) holds.
Finally, to check (Ad-iii), note that $\max_{d \geq 0}S_{\sigma,J}(i,d) = 0.$ Therefore, $\deg \lfloor 5L \rfloor  = 2 > 1 = 2 \cdot 1 - 1 + 0$.
\end{example}

@@

%\begin{rem}
%Note that $S_{\sigma,J}(i,d-1)$ as defined in condition (Ad-iii) of Definition ~\ref{defn:admissible} can equivalently be defined as $S_{\sigma,J}(i,d-1)= \{j \in J : j \neq i \text{ and }(e_j' + 2d-2)|e_i' + 2d\}.$ Written this way, $\# S_{\sigma,J}(i,d-1)$ is more apparently similar to $\mu(i,d)$ as defined in \cite[Defintion 8.5.1]{vzb:stacky}.
%\end{rem}
%\todo{Peter: I'm not sure how useful this remark is.  After seeing the definition of $S_{\sigma, J}(I,d)$ a reader will probably be a little mystified why it is a useful condition.  The inclusion of the relationship to something defined in VZB that also seems ad hoc and that they probably will not have seen may not be the most helpful use of this space.}

%\begin{lem}\label{lem:n-3s-admissible}
%Fix a genus $g$, a log divisor $\Delta$, and a coarse space $X$. Suppose $3\le r\in \BN$ so that all stacky curves $\sx'$ with $r- 1$ stacky points of degree 3 over the coarse space $X$ have all subsets $J'$ of $\{e_1, \ldots, e_{r- 1}\}$ admissible in $L'$. Then if $\sx$ has coarse space $X$, any subset of $J$ of $\{e_1, \ldots, e_r\}$ (with all $e_i =3$) is admissible viewed in $L$.
%\end{lem}
%\begin{proof}
%To show (Ad-i) and (Ad-ii) look at some $\sx'$ with $r- 1$ stacky points $'s=\{Q_1, \ldots, Q_{j - 1}, Q_{j + 1}, \ldots Q_r\}$ including a chosen $Q_i$ (and excluding some $Q_j\ne Q_i$). Then select $y_{e_r'}$ from the choice that makes the set $J'=\{i\}$ an admissible set in $\sx'$; this naturally can be seen inside of $R_{\sx}$ and satisfies (Ad-i). Furthermore, since $s$ is an admissible set of $L'$, in particular, we must have (Ad-ii) satisfied so $\frac{-\ord_{Q_l}
%^{\halfcan_X'}(y_i)}{\deg (y_i)} = 0$ for\todo{I'm confused how (Ad-ii) follows in genus 0?}
%
 %follows immediately from the base-point freeness of $3\halfcan$ which we have for the following reasons in the various genera:
%\begin{itemize}
%\item When $g> 0$, $\deg(\lfloor 3 L\rfloor)\ge 3g-3+2\ge 2g$ (the added two comes from the fact that $r\ge 2$).
%\item When $g= 0$, since $L'$ has a nontrivial admissible subset within $\{e_1, \ldots, e_{r- 1}\}$ satisfying (Ad-i), we know $\deg(\lfloor 3\lfloor)\ge 0$, so it is base-point free.
%\end{itemize}
%\end{proof}

The following Lemma will slightly strengthen condition (Ad-ii) from Definition ~\ref{defn:admissible} and this improvement is crucially used in the proof of part (c) of Lemma ~\ref{lem:raise-stacky-order}.

\begin{lem}
\label{lem:admissible_inequality}
For any $z$ as in condition (Ad-ii) of definition ~\ref{defn:admissible} the inequality (Ad-ii) implies the
tighter inequality that

@@

\begin{proof}
We know by (Ad-ii) that

@@

\begin{proof}
Each of the conditions (Ad-i), (Ad-ii), and (Ad-iii) hold for $W$
if they hold for $J$.
\end{proof}

@@

\noindent
The assumption (Ad-iii) implies
\begin{align*}
	\deg \left( e_i L' - E_i \right) \geq \max(2g - 1,0),
\end{align*}

@@

By part (a), condition (Ad-ii), and Lemma
~\ref{lem:admissible_inequality} we have
\begin{align*}
	-\ord_{Q_j}
^{\halfcan_X'}(y_{i, e_i})-\ord_{Q_j}
^{\halfcan_X'}(z)
	&\leq \frac{e_j - 1}{2} + \deg (z) \left( \subhalf{e_j'} \right) -\frac{1}{e_j'} \\
	& = \frac{e_j - 1}{2} -\frac{1}{e_j'} +\deg (z) \left( \subhalf{e_j'} \right) \\
	&= \frac{e_j(e_j -3)}{2(e_j -2)} +\deg (z) \left( \subhalf{e_j'} \right) \\
	&= \deg (y_{i, e_i}z) \subhalf{e_j'}.
\end{align*}

@@

{\bf Part (d):}
To check (d), we show (Ad-i),(Ad-ii), and (Ad-iii) are satisfied. We know (Ad-i) holds by part (b), taking the $y_{
i, e_i}$ as the generators in degree $e_i$. Next, (Ad-ii) is
strictly monotonic in the $e_i$ and hence also holds for $(\sx, J)$.
Finally, if (Ad-iii) holds for $e$ then it holds for $e + 2$ by
definition. This is where we use that (Ad-iii) holds for $d > 0$
and not just for $d = 0$.
\end{proof}

@@

\begin{longtable}
	{| c || c | c | c |}
	\hline
	Case & Signature $\sigma$ & $J$ & $e$\\
	\hline
	\hline

	(a) & (0; 3, 3, 11; 0) & \{3\} & 11\\	\hline

	(b) & (0; 3, 5, 9; 0) & \{3\}	& 9\\ \hline

	(c) & (0; 3, 7, 7; 0) & \{2, 3\}	& 7\\ \hline

	(d) & (0; 5, 5, 7; 0) & \{3\}	& 7\\ \hline

	(e) & (0; 5, 7, 7; 0) & \{2, 3\}	& 7\\ \hline

	(f) & (0; 7, 7, 7; 0) & \{1, 2, 3\}	& 7\\ \hline

	(g) & (0; 3, 3, 3, 5; 0) & \{4\} & 5\\ \hline

	(h) & (0; 3, 3, 5, 5; 0) & \{3, 4\} & 5\\ \hline

	(i) & (0; 3, 5, 5, 5; 0) & \{2, 3, 4\} & 5\\ \hline

	(j) & (0; 5, 5, 5, 5; 0) & \{1, 2, 3, 4\} & 5\\ \hline

	(k) &	(0; 3, 3, 3, 3, 3; 0) & \{1, 2, 3, 4, 5\} & 5\\ \hline

	\caption{Genus 0 Base Cases}
	\label{table:g-0-base-cases}
\end{longtable}
